Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-07 paper/paper.tex
pass on examples

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing rules. One example heuristic
function we used to rank the generated rules was \Fix{...informa um
  exemplo concreto que vc. usaram...}. The list below shows the rule
options for the top-5 rules \tname{} produces for this attack.

>>>>

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing rules. One example heuristic
function we used to rank the generated rules was
\Luc{
%\begin{wrapfigure}[14]{r}{0.5\textwidth}
\begin{figure}[H]
  \centering
%  \vspace{-7ex}
  \scalebox{0.85}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
%        \legend{relevant, irrelevant}
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rules-protocol}Number of rules per number of contents.}
%\end{wrapfigure}
\end{figure}

}

 \Fix{...informa um
  exemplo concreto que vc. usaram...}. The list below shows the rule
options for the top-5 rules \tname{} produces for this attack.
